The Astropy Project

### 2017-11-13 main.tex
period
stats edits

The \package{cosmology} package contains classes for representing different cosmologies and functions for calculating commonly used quantities such as look-back time and distance.   The package was described in detail in \cite{astropy}.  The  default cosmology in \astropy v2.0 is given by the values in \cite{2016A&A...594A..13P}

\subsection{Statistics}

The \package{astropy.stats} package provides statistical tools that
are useful for or specific to astronomy and are not found in or extend
the available functionality of other \python\ statistics packages such
as \package{scipy} \citep{scipy} or \package{statsmodels}
\citep{seabold2010statsmodels}.  The \package{stats} package contains
a range of different functionality used by many different disciplines
in astronomy.  It is not a complete set of statistic tools, but rather
a still growing collection of useful features.

The current review process for contributions to the \package{stats} package includes review of the code, documentation, testing, and scientific merit of the inclusion.  When necessary, scientific reviewers outside of the maintainers will be sought for their input on new pull requests.

In this section, we describe these tools that provide a range of different functionality including robust statistical estimators, circular statistics, periodograms, spatial statistics, and histogram binning.

@@

Robust statistics provide reliable estimates of basic statistics for complex distributions that largely mitigate the effects of outliers. The \package{stats} package includes several robust statistical functions that are commonly used in astronomy. This includes sigma clipping methods for rejecting outliers, median absolute deviation functions, and biweight estimators, which have been used to calculate the velocity dispersion of galaxy clusters \citep{Beers1990}.

@@

A set of circular statistical estimators based on \citet{JammalamadakaSengupta}
are implemented in the \package{stats} package.  These functions provide
measurements of the circular mean, variance, and moment.   For all of these
functions, they work with both \texttt{numpy.ndarrays} (assumed to be in
radians) and \texttt{Quantity} objects.  In addition, the package includes
tests for Rayleigh Test, vtest, and a function to compute the maximum likelihood estimator for the parameters of the von Mises
distribution.

\subsubsection{Lomb-Scargle Periodograms}
Periodic analysis of unevenly-spaced time series is common across subfields of Astronomy. The \package{stats} package now includes several efficient implementations of the Lomb-Scargle periodogram \citep{Lomb76, Scargle82} and several generalizations, including floating mean models \citep{Zechmeister09}, truncated Fourier models \citep{Bretthorst2003}, and appropriate handling of heteroscedastic uncertainties. Importantly, the implementations make use of several fast and scalable computational approaches \citep[e.g.][]{Press89, Palmer09}, and so can be applied to much larger datasets than Lomb-Scargle algorithms available in, e.g. \package{scipy.stats} (\citealt{scipy}). Much of the Lomb-Scargle code in AstroPy has been adapted from previously-published open-source code \citep{astroML, VanderPlas2015}.

\subsubsection{Bayesian Blocks and Histogram Binning}
AstroPy also includes an implementation of {\it Bayesian Blocks} \citep{Scargle2013}, an algorithm for analysis of break-points in non-periodic astronomical time-series. One interesting application of Bayesian Blocks is its use in determining optimal histogram binnings, and in particular binnings with unequal bin sizes. This code was adapted, with several improvements, from the \package{astroML} package \citep{astroML}. An example of a histogram fit using the Bayesian blocks algorithm is shown in the right panel of \figurename\ref{fig:bayes-blocks-hist}.

>>>>

The \package{cosmology} package contains classes for representing different cosmologies and functions for calculating commonly used quantities such as look-back time and distance.   The package was described in detail in \cite{astropy}.  The default cosmology in \astropy version 2.0 is given by the values in \cite{2016A&A...594A..13P}.

\subsection{Statistics}
% Edited by Adrian PW

The \package{astropy.stats} package provides statistical tools that
are useful for or specific to astronomy and are not found in or extend
the available functionality of other \python statistics packages such
as \package{scipy} \citep{scipy} or \package{statsmodels}
\citep{seabold2010statsmodels}.  \package{astropy.stats} contains
a range of functionality used by many different disciplines
in astronomy. It is not a complete set of statistic tools, but rather
a still growing collection of useful features.

% The current review process for contributions to the \package{astropy.stats} package includes review of the code, documentation, testing, and scientific merit of the inclusion.  When necessary, scientific reviewers outside of the maintainers will be sought for their input on new pull requests.

In this section, we describe these tools, including robust statistical estimators, circular statistics, periodograms, spatial statistics, and histogram binning.

@@

Robust statistics provide reliable estimates of basic statistics for complex distributions that largely mitigate the effects of outliers. \package{astropy.stats} includes several robust statistical functions that are commonly used in astronomy, such as sigma clipping methods for rejecting outliers, median absolute deviation functions, and biweight estimators, which have been used to calculate the velocity dispersion of galaxy clusters \citep{Beers1990}.

@@

A set of circular statistical estimators based on \citet{JammalamadakaSengupta}
are implemented in \package{astropy.stats}.  These functions provide
measurements of the circular mean, variance, and moment.   For all of these
functions, they work with both \texttt{numpy.ndarrays} (assumed to be in
radians) and \texttt{Quantity} objects.  In addition, the subpackage includes
tests for Rayleigh Test, vtest, and a function to compute the maximum likelihood
estimator for the parameters of the von Mises distribution.

\subsubsection{Lomb-Scargle Periodograms}

Periodic analysis of unevenly-spaced time series is common across many subfields of astronomy. The \package{astropy.stats} package now includes several efficient implementations of the Lomb-Scargle periodogram \citep{Lomb76, Scargle82} and several generalizations, including floating mean models \citep{Zechmeister09}, truncated Fourier models \citep{Bretthorst2003}, and appropriate handling of heteroscedastic uncertainties. Importantly, the implementations make use of several fast and scalable computational approaches \citep[e.g.,][]{Press89, Palmer09}, and so can be applied to much larger datasets than Lomb-Scargle algorithms available in, e.g., \package{scipy.stats} (\citealt{scipy}). Much of the Lomb-Scargle code in AstroPy has been adapted from previously-published open-source code \citep{astroML, VanderPlas2015}.

\subsubsection{Bayesian Blocks and Histogram Binning}
\astropypkg also includes an implementation of {\it Bayesian Blocks} \citep{Scargle2013}, an algorithm for analysis of break-points in non-periodic astronomical time-series. One interesting application of Bayesian Blocks is its use in determining optimal histogram binnings, and in particular binnings with unequal bin sizes. This code was adapted, with several improvements, from the \package{astroML} package \citep{astroML}. An example of a histogram fit using the Bayesian blocks algorithm is shown in the right panel of \figurename~\ref{fig:bayes-blocks-hist}.
